An Improved Method for Coupling Hydrodynamics with Astrophysical Reaction Networks

### 2022-04-06 simplified_sdc_intro/paper.tex
updates

We build a reaction network that approximates an $\alpha$-chain,
including all $\isotm{He}{4}$, and all of the $\alpha$ nuclei from
$\isotm{C}{12}$ to $\isotm{Ni}{56}$.  We want to capture both the
$(\alpha,\gamma)$ and $(\alpha,p)(p,\gamma)$ links, so we include the
intermediate nuclei from the $(\alpha,p)$ rate instead of
approximating these links assuming proton equilibriation.  
Following \citet{shenbildsten}, we include the sequences
$\isotm{C}{13}(\alpha,\gamma)\isotm{O}{18}(\alpha,\gamma)\isotm{Ne}{22}$
and $\isotm{N}{14}(\alpha,\gamma)\isotm{F}{18}(\alpha,
p)\isotm{Ne}{21}$, which produce the protons that can allow for
$\isotm{C}{12}(p, \gamma)\isotm{N}{13}(\alpha, p)\isotm{O}{16}$ to compete
with $\isotm{C}{12}(\alpha,\gamma)\isotm{O}{16}$.  We add $\isotm{Na}{22}$
to link the $\isotm{Ne}{21}$ produced back to the $\alpha$-chain.  We grab
all of the ReacLib \citep{reaclib} reaction rates linking these nuclei using \pynucastro~\citep{pynucastro}.
We are missing one rate each for $\isotm{C}{12} + \isotm{C}{12}$,
$\isotm{C}{12} + \isotm{O}{16}$, and $\isotm{O}{16} + \isotm{O}{16}$
    involving neutron production followed by a capture back to one of
    our $\alpha$-chain nuclei, so we explicitly add these rates as
    well.

>>>>

We build a reaction network that approximates an $\alpha$-chain,
including all $\isotm{He}{4}$, and all of the $\alpha$ nuclei from
$\isotm{C}{12}$ to $\isotm{Ni}{56}$.  We want to capture both the
$(\alpha,\gamma)$ and $(\alpha,p)(p,\gamma)$ links, so we include the
intermediate nuclei from the $(\alpha,p)$ rate instead of
approximating these links assuming proton equilibriation.  Following
\citet{shenbildsten}, we include the sequence
$\isotm{N}{14}(\alpha,\gamma)\isotm{F}{18}(\alpha, p)\isotm{Ne}{21}$,
which produce the protons that can allow for $\isotm{C}{12}(p,
\gamma)\isotm{N}{13}(\alpha, p)\isotm{O}{16}$ to compete with
$\isotm{C}{12}(\alpha,\gamma)\isotm{O}{16}$.  We add $\isotm{Na}{22}$
to link the $\isotm{Ne}{21}$ produced back to the $\alpha$-chain.  We
grab all of the ReacLib \citep{reaclib} reaction rates linking these
nuclei using \pynucastro~\citep{pynucastro}.  We are missing one rate
each for $\isotm{C}{12} + \isotm{C}{12}$, $\isotm{C}{12} +
\isotm{O}{16}$, and $\isotm{O}{16} + \isotm{O}{16}$.  These are
the sequences $\isotm{C}{12}(\isotm{C}{12}, \mathrm{n})\isotm{Mg}{23}(n, \gamma)\isotm{Mg}{24}$,
$\isotm{O}{16}(\isotm{C}{12}, \mathrm{n})\isotm{Si}{27}(n, \gamma)\isotm{Si}{28}$, and
$\isotm{O}{16}(\isotm{O}{16}, \mathrm{n})\isotm{S}{31}(n, \gamma)\isotm{S}{32}$,involving neutron
production followed by a capture back to one of our $\alpha$-chain
nuclei.  These are the only rates we approximate here, assuming
that the subsequent neutron capture is instantaneous.
